---
title: "Untitled"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(Warning = FALSE)

```

```{r packages}

library(odbc)
library(DBI)
library(ggplot2)
library(dplyr)

```

```{r connection}

con <- dbConnect(odbc(), "POC")

```

```{r data}

dat <-
  dbGetQuery(con, "SELECT [rptid]
	,[chid]
	,[rptcnty]
	,[rptdt]
	,[rptdtyr]
	,[chage]
	,[chsex]
	,CASE 
		WHEN [chracai] = 1
			AND ([chracas] + [chracbl] + [chracnh] + [chracnh] + [chracwh] = 0)
			THEN 1
		WHEN [chracas] = 1
			AND ([chracai] + [chracbl] + [chracnh] + [chracnh] + [chracwh] = 0)
			THEN 2
		WHEN [chracbl] = 1
			AND ([chracai] + [chracas] + [chracnh] + [chracnh] + [chracwh] = 0)
			THEN 3
		WHEN [chracnh] = 1
			AND ([chracai] + [chracas] + [chracbl] + [chracnh] + [chracwh] = 0)
			THEN 4
		WHEN [chracwh] = 1
			AND ([chracai] + [chracas] + [chracbl] + [chracnh] + [chracnh] = 0)
			THEN 5
		WHEN [chracai] IS NULL
			AND [chracas] IS NULL
			AND [chracbl] IS NULL
			AND [chracnh] IS NULL
			AND [chracnh] IS NULL
			AND [chracwh] IS NULL
			THEN 7
		WHEN [chracai] + [chracas] + [chracbl] + [chracnh] + [chracnh] + [chracwh] > 1
			THEN 8
		END AS raceeth
	,[chracai]
	,[chracas]
	,[chracbl]
	,[chracnh]
	,[chracnh]
	,[chracwh]
	,[chracud]
	,[cethn]
	,[chmil]
	,[chprior]
	,[chmal1]
	,[mal1lev]
	,[chmal2]
	,[mal2lev]
	,[chmal3]
	,[mal3lev]
	,[chmal4]
	,[mal4lev]
FROM (
	SELECT [rptid]
		,[chid]
		,[rptcnty]
		,[rptdt]
		,YEAR(rptdt) AS [rptdtyr]
		,[chage]
		,CASE 
			WHEN [chsex] = 1
				THEN 'male'
			WHEN [chsex] = 2
				THEN 'female'
			END AS [chsex]
		,CASE 
			WHEN [chracai] = 1
				THEN 1
			WHEN [chracai] = 2
				THEN 0
			END AS [chracai]
		,CASE 
			WHEN [chracas] = 1
				THEN 1
			WHEN [chracas] = 2
				THEN 0
			END AS [chracas]
		,CASE 
			WHEN [chracbl] = 1
				THEN 1
			WHEN [chracbl] = 2
				THEN 0
			END AS [chracbl]
		,CASE 
			WHEN [chracnh] = 1
				THEN 1
			WHEN [chracnh] = 2
				THEN 0
			END AS [chracnh]
		,CASE 
			WHEN [chracwh] = 1
				THEN 1
			WHEN [chracwh] = 2
				THEN 0
			END AS [chracwh]
		,CASE 
			WHEN [chracud] = 1
				THEN 1
			WHEN [chracud] = 2
				THEN 0
			END AS [chracud]
		--,CASE 
		--	WHEN [cethn] = 1
		--		THEN 1
		--	WHEN [cethn] = 2
		--		THEN 0
		--	END AS [cethn]
		,[cethn]
		,CASE 
			WHEN [chmil] = 1
				THEN 1
			WHEN [chmil] = 2
				THEN 0
			END [chmil]
		,[chprior]
		,[chmal1]
		,[mal1lev]
		,[chmal2]
		,[mal2lev]
		,[chmal3]
		,[mal3lev]
		,[chmal4]
		,[mal4lev]
	FROM [CA_ODS].[ndacan].[ncands_2002_2016]
	WHERE [staterr] = 'WA'
		AND YEAR([rptdt]) BETWEEN 2013
			AND 2015
		AND [rptcnty] = 53
		AND [chage] <= 6
	) AS dat
  ")

maltreatment_type <-
  dbGetQuery(con, "SELECT [cd_mal]
      ,[tx_mal]
  FROM [CA_ODS].[annual_report].[ref_ncands_mal]")

maltreatment_disposition <-
  dbGetQuery(con, "SELECT [cd_mal_lev]
      ,[tx_mal_lev]
  FROM [CA_ODS].[annual_report].[ref_ncands_mal_lev]")

```




```{r}

# aggregate data over observation period

total_children <- length(unique(dat$chid))

total_reports <- NROW(dat)

total_investigations <- length(unique(dat$rptid))

# Graphs

ages_by_year <- 
  ggplot(dat, aes(x = chage)) +
  geom_bar() +
  facet_grid(~rptdtyr)


```

The data for this request comes from the NDCANDS child file. You can find more information on [NCANDS here](https://www.ndacan.cornell.edu/datasets/pdfs_user_guides/Dataset210NCANDSChildFileUserGuideFY2016.pdf) and a [code book here](https://www.ndacan.cornell.edu/datasets/pdfs_user_guides/NCANDSChildFileCodebook.pdf). NCANDS submissions are based around the Federal Fiscal Year (2016) with the most recent submission from FFY 2016. Because states don't include information from open investigations, the last few months of each file is missing a siginifcant number of reports. This data will be included in subseqent reports but makes the most recent data set incomplete. As a result, the data included in this request is from between calendar year 2013 through 2015.
